Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-15 latex/article.tex
moving files

\documentclass{llncs}
\usepackage{enumerate}% http://ctan.org/pkg/enumerate
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage{url}
\usepackage{overpic}
\usepackage{enumerate}
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{tikz}        % standard LaTeX graphics tool
\usetikzlibrary{arrows}
\usetikzlibrary{quotes,angles}
\usepackage{subfigure}                                 % authors: subfigures
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}   % authors: last version of algorithm display
\usepackage{todonotes}

@@

\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1}\and  David Coeurjolly\inst{1}\and   Jean-Philippe Farrugia\inst{1}\and Jean-Claude Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{2} }

>>>>

\documentclass{llncs}
\usepackage{enumerate}% http://ctan.org/pkg/enumerate
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage{url}
\usepackage{overpic}
\usepackage{enumerate}
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{tikz}        % standard LaTeX graphics tool
%\usetikzlibrary{arrows}
%\usetikzlibrary{quotes,angles}
\usepackage{subfigure}                                 % authors: subfigures
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}   % authors: last version of algorithm display
\usepackage{todonotes}

@@

\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1,2}\and David
Coeurjolly\inst{1}\and Jean-Philippe Farrugia\inst{1}\and Jean-Claude
Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{2} }
